%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}
\vspace{1.5mm}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {\large \textbf {\href{https://github.com/snehsagarajput/sudoku-solver-app}{Sudoku Solver Android Application}}} % Job title
    {} % Organization
    {} % Location
    {} % Date(s)
    {\vspace{-1.5mm}
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \setstretch{1.25}
        \item {Developed an Android Application with React-Native.}
        \item{Application can extract Sudoku Puzzle from an image using Machine Learning algorithms in order to solve it.}
        %\item {Implemented a newer mixed algorithm for extracting Sudoku Puzzle.}
        \item {Implemented algorithm is faster and accurate than most of the existing algorithms.}
        \item {Implemented backtracking and combination based algorithms to solve extracted Sudoku.}
      \end{cvitems}
   \vspace{1.5mm} }

%---------------------------------------------------------
\end{cventries}

\begin{cventries}

%---------------------------------------------------------
  \cventry
    {\large \textbf {\href{https://github.com/snehsagarajput/fintech-order-management-webapp}{FinTech B2B Order Management Application}}} % Job title
    {} % Organization
    {} % Location
    {} % Date(s)
    {\vspace{-1.5mm}
      \begin{cvitems} % Description(s) of tasks/responsibilities
       \setstretch{1.25}
        \item {Developed an Web Application with ReactJS and JAVA backend.}
        \item{Developed order dashboard with different user level login capability.}
        \item {Implemented dynamic search, pagination, add and edit features for order management.}
        \item {Designed responsive and interactive dynamic web pages.}
      \end{cvitems}
  \vspace{1.5mm} }

%---------------------------------------------------------
\end{cventries}

\begin{cventries}

%---------------------------------------------------------
  \cventry
    {\large \textbf{\href{https://github.com/snehsagarajput/nst-app}{Neural Style Transfer Web Application}}} % Job title
    {} % Organization
    {} % Location
    {} % Date(s)
    {\vspace{-1.5mm}
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \setstretch{1.25}
        %\item{Implemented the research paper "Perceptual Losses for Real- Time Style Transfer and Super-Resolution" by Johnson et al.}
        \item {Implemented a research paper by developing a Web Application with React-JS.}
        \item {Trained a Neural Network which can manipulate digital images in order to adopt the appearance or visual style of other images.}
        \item {Deployed the trained model on a Flask Server.}
      \end{cvitems}
   \vspace{1.5mm} }

%---------------------------------------------------------
\end{cventries}


\begin{cventries}

%---------------------------------------------------------
  \cventry
    {\large \textbf{\href{https://github.com/snehsagarajput/darknet}{Alert System for  Social Distancing and Face Mask Detection}}} % Job title
    {} % Organization
    {} % Location
    {} % Date(s)
    {\vspace{-1.5mm}
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \setstretch{1.25}
        \item {Created a solution to identify if people are wearing face masks and following social distancing norms.}
        \item {Used state of art algorithm YOLO (You Only Look Once) Version 4 to generate the deep learning model.}
        \item {The platform can generate notifications to warn if anyone is found violating norms.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
